---
title: "trial_simulation_06_27"
author: "Yiling Liu"
date: "7/3/2017"
output: pdf_document
---

```{r, warning=FALSE, message=FALSE}
# load library and source function
library("GoFKernel")
library("cmprsk")
library(xlsx)
library("binom")
library("survival")
library(Gmisc)
library(xtable)
setwd("~/COMET_trial/COMET_trial_simulation/COMET_trial_6_12")
source("trial_simulation_06_24.R")
```

Finish the code for the trial simulations. There should be three different types of trials: AS vs Lx, AS vs Lx+Rx, AS vs GCC, where GCC is the one where women choose randomly which treatment option (Lx, Lx+Rx, Mx)
```{r, warning=FALSE, message=FALSE}
#both have to use output from cumic function!!!!!
#for LO compare to AS
#for AS
N <- 10000
psi <- 0.7
ti=10
deltat=1/12
beta=0.8
psi=0.7
rho=0.19
lambda=0.1

u <- sample(c(0,1),N,prob=c(rho,1-rho),replace = TRUE)
#assume 0 is wrong diagnosis and 1 is right diagnosis
u[u==1] <- sample(c(1,Inf),sum(u==1),prob=c(psi,1-psi),replace = TRUE)  
#assume 1 is finite  and Inf is inf
u[u==1] <- sample(rexp(N,lambda),sum(u==1)) 

rand_vect_cont <- function(n=4,N) 
{
  ma <- NULL
  for(i in 1:N)
  {
  vec <- runif(n)
  ma<- rbind(vec/sum(vec),ma)
  }
  return(ma)
}

ma3 <- rand_vect_cont(3,N)
prob.as.con <- ma3[,1]
year.as.con <- fun.inver(prob.as.con,3)

as.time <- rep(NA,length(N))
as.type <- rep(NA,length(N))

for (i in 1:N)
{
  as.time[i] <- min(year.as.con,u)
  
  if (as.time[i]==u[i])
  {
    as.type[i] <- "Ipsilateral Invasive"
  }
  if (as.time[i]==year.as.con[i])
  {
    as.type[i] <- "Contralateral Cancer"
  }
}





#for LO
N <- 10000
ma.lo <- rand_vect_cont(4,N)

prob.alllo.inva <- runif(N,0,1)    #ma.lo[,1]
prob.alllo.dcis <- runif(N,0,1)    #ma.lo[,2]
prob.alllo.con <-  runif(N,0,1)    #ma.lo[,3]

#for ipsilateral invasive cancer recurrence
allLO.inva <- fun.inver(prob.alllo.inva,1)
#for ipsilateral dcis recurrence
allLO.dcis <- fun.inver(prob.alllo.dcis,2)
#for Contralateral recurrence
allLO.con <- fun.inver(prob.alllo.con,3)

allLO.time <- rep(NA,N)
allLO.type <- rep(NA,N)

for (i in 1:N)
{
  allLO.time[i] <- min(allLO.inva[i],allLO.dcis[i],allLO.con[i])
  if (allLO.time[i]==allLO.inva[i])
  {
    allLO.type[i] <- "Ipsilateral Invasive"
  }
  if (allLO.time[i]==allLO.dcis[i])
  {
    allLO.type[i] <- "Ipsilateral DCIS"
  }
  if (allLO.time[i]==allLO.con[i])
  {
    allLO.type[i] <- "Contralateral Cancer"
  }
}



#for LO
T <- seq(0,60,0.001)
ss.LO <- allLO.time
gg.LO <- factor(allLO.type,c("Ipsilateral Invasive","Ipsilateral DCIS","Contralateral Cancer"))
print(xx.LO <- cuminc(ss.LO,gg.LO))
plot(xx.LO,main="Cumulative Incidence Risk for Competing Risk",col=1:3,xlim=c(0,20))

T <- seq(0.1,60,0.5)
fun.AS <- function(u)
{
  AS.value <- rep(NA,length(u))
  for(j in 1:length(u))
  {
    AS.value[j] <- cum.cal(ti=u[j],deltat=1/12,N7=10000,n.sim = 1,
                           beta=0.8,psi=0.7,rho=0.19,lambda=0.1)$mean.pro
  }
  return(AS.value)
}

cum.inva.AS <- fun.AS(c(T))

plot(c(0,T), c(0,cum.inva.AS),
     main = "Cumulative Incidence rate for Ipsilateral invasive cancer",lty=1,type='l',xlab="Years",
     ylab="Cumulative incidence",
     pch=1,col="blue",ylim=c(0,1),xlim=c(0,20))

par(new=TRUE)
plot(xx.LO$`1 Ipsilateral Invasive`$time,xx.LO$`1 Ipsilateral Invasive`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Ipsilateral invasive cancer",
     ylim=c(0,1),xlim=c(0,20))

legend("topright",
       legend=c("Lumpectomy Arm","AS Arm"),
       col =c("red","blue"),inset=.02,cex=0.5,lty =1)


#for LRT
#for ipsilateral Invasive cancer
#for LO
N <- 10000
ma.lrt <- rand_vect_cont(4,N)

prob.alllrt.inva <- runif(N,0,1)  #ma.lrt[,1]
prob.alllrt.dcis <-runif(N,0,1)  #ma.lrt[,2]
prob.alllrt.con <- runif(N,0,1)   #ma.lrt[,3]

#for ipsilateral invasive cancer recurrence
allLrt.inva <- fun.inver(prob.alllrt.inva,4)
#for ipsilateral dcis recurrence
allLrt.dcis <- fun.inver(prob.alllrt.dcis,5)
#for Contralateral recurrence
allLrt.con <- fun.inver(prob.alllrt.con,6)

allLrt.time <- rep(NA,N)
allLrt.type <- rep(NA,N)

for (i in 1:N)
{
  allLrt.time[i] <- min(allLrt.inva[i],allLrt.dcis[i],allLrt.con[i])
  if (allLrt.time[i]==allLrt.inva[i])
  {
    allLrt.type[i] <- "Ipsilateral Invasive"
  }
  if (allLrt.time[i]==allLrt.dcis[i])
  {
    allLrt.type[i] <- "Ipsilateral DCIS"
  }
  if (allLrt.time[i]==allLrt.con[i])
  {
    allLrt.type[i] <- "Contralateral Cancer"
  }
}


T <- seq(0,60,0.001)
ss.Lrt <- allLrt.time
gg.Lrt <- factor(allLrt.type,c("Ipsilateral Invasive","Ipsilateral DCIS","Contralateral Cancer"))
print(xx.Lrt <- cuminc(ss.Lrt,gg.Lrt))
plot(xx.Lrt,main="Cumulative Incidence Risk for Competing Risk in LRT group",col=1:3,xlim=c(0,20))


T <- seq(0.1,60,0.5)
plot(c(0,T), c(0,cum.inva.AS),
     main = "Cumulative Incidence rate for Ipsilateral invasive cancer",lty=1,type='l',xlab="Years",
     ylab="Cumulative incidence",
     pch=1,col="blue",ylim=c(0,1),xlim=c(0,20))

par(new=TRUE)
plot(xx.Lrt$`1 Ipsilateral Invasive`$time,xx.Lrt$`1 Ipsilateral Invasive`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Ipsilateral invasive cancer",
     ylim=c(0,1),xlim=c(0,20))

legend("topright",
       legend=c("Lumpectomy+Radiation Arm","AS Arm"),
       col =c("red","blue"),inset=.02,cex=0.5,lty =1)


#compare LRT and AS for Contralateral Invasive
plot(xx.LO$`1 Contralateral Cancer`$time,xx.LO$`1 Contralateral Cancer`$est,lty=1,col="blue",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Contralateral cancer",
     ylim=c(0,1),xlim=c(0,20))
par(new=TRUE)
plot(xx.Lrt$`1 Contralateral Cancer`$time,xx.Lrt$`1 Contralateral Cancer`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Contralateral cancer",
     ylim=c(0,1),xlim=c(0,20))

legend("topright",
       legend=c("Lumpectomy+Radiation Arm","AS Arm"),
       col =c("red","blue"),inset=.02,cex=0.5,lty =1)


#rescale the proportion
#Mastectomy 27.1%
#lumpectomy 20.8%
#Lumpectomy + Radiation 52.1%
library("gtools")

N <- 10000
index.vector <- sample(c(1,2,3), N, prob=c(0.271,0.208,0.521),replace = TRUE)
#1 for Mastectomy
#2 for lumpectomy
#3 for Lumpectomy + Radiation

#check correct or not
sum(index.vector==1)
sum(index.vector==2)
sum(index.vector==3)

#for each woman generate the history according to the group
#each group contain two things, time to event, type of event

index.mx <- which(index.vector==1)
index.lx <- which(index.vector==2)
index.lrt <- which(index.vector==3)


#for lumpectomy group

#function to draw random probability for each competing risk
rand_vect_cont <- function(n=4,N) 
{
  ma <- NULL
  for(i in 1:N)
  {
  vec <- runif(n)
  ma<- rbind(vec/sum(vec),ma)
  }
  return(ma)
}

ma1 <- rand_vect_cont(4,length(index.lx))

prob.lo.inva <- runif(length(index.lx),0,1) #ma1[,1]
prob.lo.dcis <- runif(length(index.lx),0,1) #ma1[,2]
prob.lo.con <- runif(length(index.lx),0,1) #ma1[,3]

#for ipsilateral invasive cancer recurrence
year.lo.inva <- fun.inver(prob.lo.inva,1)
#for ipsilateral dcis recurrence
year.lo.dcis <- fun.inver(prob.lo.dcis,2)
#for Contralateral recurrence
year.lo.con <- fun.inver(prob.lo.con,3)


#contain two things, time to event, type of event
Lo.time <- rep(NA,length(index.lx))
Lo.type <- rep(NA,length(index.lx))


for (i in 1:length(index.lx))
{
  Lo.time[i] <- min(year.lo.inva[i],year.lo.dcis[i],year.lo.con[i])
  if (Lo.time[i]==year.lo.inva[i])
  {
    Lo.type[i] <- "Ipsilateral Invasive"
  }
  if (Lo.time[i]==year.lo.dcis[i])
  {
    Lo.type[i] <- "Ipsilateral DCIS"
  }
  if (Lo.time[i]==year.lo.con[i])
  {
    Lo.type[i] <- "Contralateral Cancer"
  }
}


#for Lumpectomy + Radiation
ma2 <- rand_vect_cont(4,length(index.lrt))

prob.lrt.inva <-runif(length(index.lrt),0,1) #ma2[,1]
prob.lrt.dcis <-runif(length(index.lrt),0,1) #ma2[,2]
prob.lrt.con <- runif(length(index.lrt),0,1) #ma2[,3]

#for ipsilateral invasive cancer recurrence
year.lrt.inva <- fun.inver(prob.lrt.inva,4)
#for ipsilateral dcis recurrence
year.lrt.dcis <- fun.inver(prob.lrt.dcis,5)
#for Contralateral recurrence
year.lrt.con <- fun.inver(prob.lrt.con,6)


#contain two things, time to event, type of event
Lrt.time <- rep(NA,length(index.lrt))
Lrt.type <- rep(NA,length(index.lrt))


for (i in 1:length(index.lrt))
{
  Lrt.time[i] <- min(year.lrt.inva[i],year.lrt.dcis[i],year.lrt.con[i])
  if (Lrt.time[i]==year.lrt.inva[i])
  {
    Lrt.type[i] <- "Ipsilateral Invasive"
  }
  if (Lrt.time[i]==year.lrt.dcis[i])
  {
    Lrt.type[i] <- "Ipsilateral DCIS"
  }
  if (Lrt.time[i]==year.lrt.con[i])
  {
    Lrt.type[i] <- "Contralateral Cancer"
  }
}

#1 for Mastectomy
#foor Mx with constant hazard lambda
#P(rec@10 years)=0.01=1-e^{-10*lambda}
#rate for ipsilateral invasive
#rate for ipsilateral DCIS equal to 0
#so time to event must be ipsilateral invasive, not ipsilateral dcis and contralateral cancer
harz <- log(0.99)/(-10)
mx.time <- rexp(length(index.mx),rate=harz)
mx.type <- rep("Ipsilateral Invasive",length(index.mx))

lrm.time <- c(Lo.time,Lrt.time,mx.time)
lrm.type <- c(Lo.type,Lrt.type,mx.type)

T <- seq(0,60,0.001)
ss.lrm <- lrm.time
gg.lrm <- factor(lrm.type,c("Ipsilateral Invasive","Ipsilateral DCIS","Contralateral Cancer"))
print(xx.lrm <- cuminc(ss.lrm,gg.lrm))
plot(xx.lrm,main="Cumulative Incidence Risk for Competing Risk in Mixed group",col=1:3,xlim=c(0,20))

#Compare Mixed to AS in ipsilateral Invasive
T <- seq(0.1,60,0.5)
plot(c(0,T), c(0,cum.inva.AS),
     main = "Cumulative Incidence rate for Ipsilateral invasive cancer",lty=1,type='l',xlab="Years",
     ylab="Cumulative incidence",
     pch=1,col="blue",ylim=c(0,1),xlim=c(0,20))

par(new=TRUE)
plot(xx.lrm$`1 Ipsilateral Invasive`$time,xx.lrm$`1 Ipsilateral Invasive`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Ipsilateral invasive cancer",
     ylim=c(0,1),xlim=c(0,20))

legend("topright",
       legend=c("Lumpectomy+Radiation+Mastectomy Arm","AS Arm"),
       col =c("red","blue"),inset=.02,cex=0.5,lty =1)



#Compare Mixed to AS in Contralateral cancer
plot(xx.LO$`1 Contralateral Cancer`$time,xx.LO$`1 Contralateral Cancer`$est,lty=1,col="blue",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Contralateral cancer",
     ylim=c(0,1),xlim=c(0,20))
par(new=TRUE)
plot(xx.lrm$`1 Contralateral Cancer`$time,xx.lrm$`1 Contralateral Cancer`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Cumulative incidence",main="Cumulative Incidence rate for Contralateral cancer",
     ylim=c(0,1),xlim=c(0,20))

legend("topright",
       legend=c("Lumpectomy+Radiation Arm","AS Arm"),
       col =c("red","blue"),inset=.02,cex=0.5,lty =1)

```


At 2, 5 and 10 years, compute ipsilateral disease-free survival and CI for both AS and ‘control arm’ (Lx/Lx+Rx/Mx), based on KM
```{r results = 'asis'}
knitr::opts_chunk$set(cache=TRUE)
#At 2, 5 and 10 years, compute ipsilateral disease-free survival and CI for both AS 
#and ‘control arm’ (Lx/Lx+Rx/Mx), based on KM
#for LO
event <- allLO.type
event <- ifelse(event=="Ipsilateral Invasive",1,0)
time <- allLO.time
id <- 1:N
mydat <- data.frame(id, time, event)
#Surv(mydat$time, mydat$event)
fit1 <- survfit(Surv(mydat$time, mydat$event)~1 ,data=mydat)

#for Lumpectomy and Radiation
event2 <- allLrt.type
event2 <- ifelse(event2=="Ipsilateral Invasive",1,0)
time2 <- allLrt.time
id2 <- 1:N
mydat2 <- data.frame(id2, time2, event2)
fit2<- survfit(Surv(mydat2$time2, mydat2$event2)~1 ,data=mydat2)


#for GCC
event3 <- lrm.type
event3 <- ifelse(event3=="Ipsilateral Invasive",1,0)
time3 <- lrm.time
id3 <- 1:N
mydat3 <- data.frame(id3, time3, event3)
fit3<- survfit(Surv(mydat3$time3, mydat3$event3)~1 ,data=mydat3)

#use KM estimator and also get CI
#extract confidence interval
#for Lumpectomy
#for year2
lo.ci.2 <- paste(round(mean(fit1$surv[round(fit1$time,2)==2]),3),"(",
                 round(mean(fit1$lower[round(fit1$time,2)==2]),3),",",
                 round(mean(fit1$upper[round(fit1$time,2)==2]),3),")")
#for year5
lo.ci.5 <- paste(round(mean(fit1$surv[round(fit1$time,2)==5]),3),"(",
                 round(mean(fit1$lower[round(fit1$time,2)==5]),3),",",
                 round(mean(fit1$upper[round(fit1$time,2)==5]),3),")")
#for year10
lo.ci.10 <- paste(round(mean(fit1$surv[round(fit1$time,2)==10]),3),"(",
                  round(mean(fit1$lower[round(fit1$time,2)==10]),3),",",
                  round(mean(fit1$upper[round(fit1$time,2)==10]),3),")")


#for Lumpectomy+Radiation
#for year2
lrt.ci.2 <- paste(round(mean(fit2$surv[round(fit2$time,2)==2]),3),"(",
                  round(mean(fit2$lower[round(fit2$time,2)==2]),3),",",
                  round(mean(fit2$upper[round(fit2$time,2)==2]),3),")")

#for year5
lrt.ci.5 <- paste(round(mean(fit2$surv[round(fit2$time,1)==5]),3),"(",
                  round(mean(fit2$lower[round(fit2$time,1)==5]),3),",",
                  round(mean(fit2$upper[round(fit2$time,1)==5]),3),")")

#for year10
lrt.ci.10 <- paste(round(mean(fit2$surv[round(fit2$time,1)==10]),3),"(",
                   round(mean(fit2$lower[round(fit2$time,1)==10]),3),",",
                   round(mean(fit2$upper[round(fit2$time,1)==10]),3),")")


#for Lumpectomy+Radiation+Matectomy
#for year2
lrm.ci.2 <- paste(round(mean(fit3$surv[round(fit3$time,2)==2]),3),"(",
                  round(mean(fit3$lower[round(fit3$time,2)==2]),3),",",
                  round(mean(fit3$upper[round(fit3$time,2)==2]),3),")")

#for year5
lrm.ci.5 <- paste(round(mean(fit3$surv[round(fit3$time,2)==5]),3),"(",
                  round(mean(fit3$lower[round(fit3$time,2)==5]),3),",",
                  round(mean(fit3$upper[round(fit3$time,2)==5]),3),")")

#for year10
lrm.ci.10 <- paste(round(mean(fit3$surv[round(fit3$time,1)==10]),3),"(",
                   round(mean(fit3$lower[round(fit3$time,1)==10]),3),",",
                   round(mean(fit3$upper[round(fit3$time,1)==10]),3),")")


#AS
#Estimate fraction for AS
setwd("~/COMET_trial/COMET_trial_simulation/COMET_trial_6_12")
source("AS functions.R")
ASest.2 <- cum.cal(ti=2,deltat=1/12,N7=10000,n.sim = 5,
                   beta=0.8,psi=0.7,rho=0.19,lambda=0.1)$mean.pro

ASest.5 <- cum.cal(ti=5,deltat=1/12,N7=10000,n.sim = 5,
                   beta=0.8,psi=0.7,rho=0.19,lambda=0.1)$mean.pro

ASest.10 <- cum.cal(ti=10,deltat=1/12,N7=10000,n.sim = 5,
                    beta=0.8,psi=0.7,rho=0.19,lambda=0.1)$mean.pro


#CI
AS.est.ci <- rbind(binom.confint(round(N*ASest.2),N,level=0.95,methods = "exact"),
                   binom.confint(round(N*ASest.5),N,level=0.95,methods = "exact"),
                   binom.confint(round(N*ASest.10),N,level=0.95,methods = "exact"))[,4:6]

#CI for disearse-free survival
AS.ci.sur <- 1-AS.est.ci
AS.ci.sur <- AS.ci.sur[,c(1,3,2)]
names(AS.ci.sur) <- names(AS.ci.sur)[c(1,3,2)]


#for year2
as.ci.2 <- paste(round(AS.ci.sur[1,1],3),"(",
                  round(AS.ci.sur[1,2],3),",",
                  round(AS.ci.sur[1,3],3),")")

#for year5
as.ci.5 <- paste(round(AS.ci.sur[2,1],3),"(",
                  round(AS.ci.sur[2,2],3),",",
                  round(AS.ci.sur[2,3],3),")")


#for year10
as.ci.10 <- paste(round(AS.ci.sur[3,1],3),"(",
                  round(AS.ci.sur[3,2],3),",",
                  round(AS.ci.sur[3,3],3),")")

LO.km <- c(lo.ci.2,lo.ci.5,lo.ci.10)
lrt.km <- c(lrt.ci.2,lrt.ci.5,lrt.ci.10)
lrm.km <- c(lrm.ci.2,lrm.ci.5,lrm.ci.10)
as.km <- c(as.ci.2,as.ci.5,as.ci.10)
KM <- data.frame(LO.km,lrt.km,lrm.km,as.km)
colnames(KM)[1] <- "K-M Estimator for Lx"
colnames(KM)[2] <- "K-M Estimator for LRT"
colnames(KM)[3] <- "K-M Estimator for LRT+Mx"
colnames(KM)[4] <- "K-M Estimator for AS"


rownames(KM)[1] <- "Year2"
rownames(KM)[2] <- "Year5"
rownames(KM)[3] <- "Year10"

options(xtable.comment = FALSE)
KM <- xtable(KM,caption = "KM estimator and Confidence Interval for Ipsilateral Cancer-free Survival")
print(KM,sanitize.text.function=function(x){x})
```


Do a competing risk analysis where you compute cumultative incidence of ipsilateral disease and CI (use cuminc) for both AS and ‘control arm’ [same as above, but do competing risk instead of KM
```{r results = 'asis'}
knitr::opts_chunk$set(cache=TRUE)
#Do a competing risk analysis where you compute cumultative incidence 
#of ipsilateral disease and CI
xx.lrt.time <- xx.Lrt$`1 Ipsilateral Invasive`$time
xx.lrt.est <- xx.Lrt$`1 Ipsilateral Invasive`$est


mean(xx.lrt.est[round(xx.lrt.time,2)==2])

#use cuminc and also get CI
#extract confidence interval
#for Lumpectomy
#for year2
set.seed(123)
xx.lO.time <- xx.LO$`1 Ipsilateral Invasive`$time
xx.lO.est <- xx.LO$`1 Ipsilateral Invasive`$est

LO.cum.2 <- mean(xx.lO.est[round(xx.lO.time,2)==2])
LO.cum.5 <- mean(xx.lO.est[round(xx.lO.time,1)==5])
LO.cum.10 <- mean(xx.lO.est[round(xx.lO.time,1)==10])

N <- 10000
Lo.cumest.ci <- rbind(binom.confint(round(N*LO.cum.2),N,level=0.95,methods = "exact"),
                   binom.confint(round(N*LO.cum.5),N,level=0.95,methods = "exact"),
                   binom.confint(round(N*LO.cum.10),N,level=0.95,methods = "exact"))[,4:6]


#for year2
Lo.cumest.ci.2 <- paste(round(Lo.cumest.ci[1,1],3),"(",
                 round(Lo.cumest.ci[1,2],3),",",
                 round(Lo.cumest.ci[1,3],3),")")

#for year5
Lo.cumest.ci.5 <- paste(round(Lo.cumest.ci[2,1],3),"(",
                        round(Lo.cumest.ci[2,2],3),",",
                        round(Lo.cumest.ci[2,3],3),")")


#for year10
Lo.cumest.ci.10 <- paste(round(Lo.cumest.ci[3,1],3),"(",
                        round(Lo.cumest.ci[3,2],3),",",
                        round(Lo.cumest.ci[3,3],3),")")


#for Lumpectomy+Radiation
#for year2
set.seed(123)
xx.lrt.time <- xx.Lrt$`1 Ipsilateral Invasive`$time
xx.lrt.est <- xx.Lrt$`1 Ipsilateral Invasive`$est

Lrt.cum.2 <- mean(xx.lrt.est[round(xx.lrt.time,2)==2])
Lrt.cum.5 <- mean(xx.lrt.est[round(xx.lrt.time,1)==5])
Lrt.cum.10 <- mean(xx.lrt.est[round(xx.lrt.time)==10])


Lrt.cumest.ci <- rbind(binom.confint(round(N*Lrt.cum.2),N,level=0.95,methods = "exact"),
                      binom.confint(round(N*Lrt.cum.5),N,level=0.95,methods = "exact"),
                      binom.confint(round(N*Lrt.cum.10),N,level=0.95,methods = "exact"))[,4:6]


#for year2
Lrt.cumest.ci.2 <- paste(round(Lrt.cumest.ci[1,1],3),"(",
                        round(Lrt.cumest.ci[1,2],3),",",
                        round(Lrt.cumest.ci[1,3],3),")")

#for year5
Lrt.cumest.ci.5 <- paste(round(Lrt.cumest.ci[2,1],3),"(",
                        round(Lrt.cumest.ci[2,2],3),",",
                        round(Lrt.cumest.ci[2,3],3),")")


#for year10
Lrt.cumest.ci.10 <- paste(round(Lrt.cumest.ci[3,1],3),"(",
                         round(Lrt.cumest.ci[3,2],3),",",
                         round(Lrt.cumest.ci[3,3],3),")")






#for Lumpectomy+Radiation+Matectomy
set.seed(123)
xx.lrm.time <- xx.lrm$`1 Ipsilateral Invasive`$time
xx.lrm.est <- xx.lrm$`1 Ipsilateral Invasive`$est

Lrm.cum.2 <- mean(xx.lrm.est[round(xx.lrm.time,1)==2])
Lrm.cum.5 <- mean(xx.lrm.est[round(xx.lrm.time,1)==5])
Lrm.cum.10 <- mean(xx.lrm.est[round(xx.lrm.time,1)==10])


Lrm.cumest.ci <- rbind(binom.confint(round(N*Lrm.cum.2),N,level=0.95,methods = "exact"),
                       binom.confint(round(N*Lrm.cum.5),N,level=0.95,methods = "exact"),
                       binom.confint(round(N*Lrm.cum.10),N,level=0.95,methods = "exact"))[,4:6]


#for year2
Lrm.cumest.ci.2 <- paste(round(Lrm.cumest.ci[1,1],3),"(",
                         round(Lrm.cumest.ci[1,2],3),",",
                         round(Lrm.cumest.ci[1,3],3),")")

#for year5
Lrm.cumest.ci.5 <- paste(round(Lrm.cumest.ci[2,1],3),"(",
                         round(Lrm.cumest.ci[2,2],3),",",
                         round(Lrm.cumest.ci[2,3],3),")")


#for year10
Lrm.cumest.ci.10 <- paste(round(Lrm.cumest.ci[3,1],3),"(",
                          round(Lrm.cumest.ci[3,2],3),",",
                          round(Lrm.cumest.ci[3,3],3),")")




#AS
#Estimate fraction for AS




#for year2
as.cumci.2 <- paste(round(AS.est.ci[1,1],3),"(",
                 round(AS.est.ci[1,2],3),",",
                 round(AS.est.ci[1,3],3),")")

#for year5
as.cumci.5 <- paste(round(AS.est.ci[2,1],3),"(",
                 round(AS.est.ci[2,2],3),",",
                 round(AS.est.ci[2,3],3),")")


#for year10
as.cumci.10 <- paste(round(AS.est.ci[3,1],3),"(",
                     round(AS.est.ci[3,2],3),",",
                     round(AS.est.ci[3,3],3),")")


LO.cum <- c(Lo.cumest.ci.2,Lo.cumest.ci.5,Lo.cumest.ci.10)
lrt.cum <- c(Lrt.cumest.ci.2,Lrt.cumest.ci.5,Lrt.cumest.ci.10)
lrm.cum <- c(Lrm.cumest.ci.2,Lrm.cumest.ci.5,Lrm.cumest.ci.10)
as.cum <- c(as.cumci.2,as.cumci.5,as.cumci.10)

CUM <- data.frame(LO.cum,lrt.cum,lrm.cum,as.cum)

colnames(CUM)[1] <- "Rate for Lx"
colnames(CUM)[2] <- "Rate for LRT"
colnames(CUM)[3] <- "Incidence Rate LRT+Mx"
colnames(CUM)[4] <- "Incidence Rate for AS"


rownames(CUM)[1] <- "Year2"
rownames(CUM)[2] <- "Year5"
rownames(CUM)[3] <- "Year10"
options(xtable.comment = FALSE)

CUM <- xtable(CUM,caption = "Cumulative Incidence Rate for Ipsilateral Invasive Cancer")
print(CUM,sanitize.text.function=function(x){x})
```