---
title: "trial_simulation_rmd_6_12"
author: "Yiling Liu"
date: "6/15/2017"
output: pdf_document
---

**Firstly we use "graphclick" to get observed data from papers and store the observed data in xlsx files.**

Then we read in the file.
```{r results = 'asis'}
#Sampling from an Arbitrary Density
#generating sample numbers at random from any probability distribution given its cumulative distribution function.
#read in the observe data draw from the figure
library("GoFKernel")
library("cmprsk")
library(xlsx)
setwd("~/Desktop/function3")
raw.LO.inva <- read.xlsx("points of LO.xlsx",sheetIndex=1)
LO.xy.inva <- raw.LO.inva[,1:2]
raw.LRT.inva <- read.xlsx("LRT_inva.xlsx",sheetIndex=1)
LRT.xy.inva <- raw.LRT.inva[,1:2]
raw.LO.dcis <- read.xlsx("LO_dcis.xlsx",sheetIndex=1)
LO.xy.dcis <- raw.LO.dcis[,1:2]
raw.LRT.dcis <- read.xlsx("LRT_dcis.xlsx",sheetIndex=1)
LRT.xy.dcis <- raw.LRT.dcis[,1:2]
raw.LO.con <- read.xlsx("LO.con.xlsx",sheetIndex=1)
LO.xy.con <- raw.LO.con[,1:2]
raw.LRT.con <- read.xlsx("LRT.con.xlsx",sheetIndex=1)
LRT.xy.con <- raw.LRT.con[,1:2]
```

**Then I use linear interpolation. Here I use graph to show the result.**
```{r results = 'asis'}
#linear interpolation
fun.LO.inva <- approxfun(x=c(0,LO.xy.inva$x,60),y=c(0,LO.xy.inva$y/100,1), method="linear")
fun.LO.dcis <- approxfun(x=c(0,LO.xy.dcis$x,60),y=c(0,LO.xy.dcis$y/100,1), method="linear")
fun.LO.con <- approxfun(x=c(0,LO.xy.con$x,60),y=c(0,LO.xy.con$y/100,1), method="linear")

fun.LRT.inva <- approxfun(x=c(0,LRT.xy.inva$x,60),y=c(0,LRT.xy.inva$y/100,1), method="linear")
fun.LRT.dcis <- approxfun(x=c(0,LRT.xy.dcis$x,60),y=c(0,LRT.xy.dcis$y/100,1), method="linear")
fun.LRT.con <- approxfun(x=c(0,LRT.xy.con$x,60),y=c(0,LRT.xy.con$y/100,1), method="linear")

#get the inverse of these function
inver.LO.inva <- inverse(fun.LO.inva,lower=0,upper=60)
inver.LO.dcis <- inverse(fun.LO.dcis,lower=0,upper=60)
inver.LO.con <- inverse(fun.LO.con,lower=0,upper=60)

inver.LRT.inva <- inverse(fun.LRT.inva,lower=0,upper=60)
inver.LRT.dcis <- inverse(fun.LRT.dcis,lower=0,upper=60)
inver.LRT.con <- inverse(fun.LRT.con,lower=0,upper=60)
```

Since we want to input a vector of time and also return a vector. We user define a new function.
```{r results = 'asis'}
#return a list of output from the function
#1 for LO.inva
#2 for LO.dcis
#3 for LO.con
#4 for LRT.inva
#5 for LRT.dcis
#5 fot LRT.con
fun.all <- function(u,type)
{
  if(type==1)
  {
    fun = fun.LO.inva
  }
  if(type==2)
  {
    fun = fun.LO.dcis
  }
  if(type==3)
  {
    fun = fun.LO.con
  }
  if(type==4)
  {
    fun = fun.LRT.inva
  }
  if(type==5)
  {
    fun = fun.LRT.dcis
  }
  if(type==6)
  {
    fun = fun.LRT.con
  }
  y.value <- rep(NA,length(u))
  for(j in 1:length(u))
  {
    y.value[j] <- fun(u[j])
  }
  return(y.value)
}
```

Then we compare empirical cdf from simulation to the true cdf
For Cumulative incidence rate of Invasive LO
```{r results = 'asis'}
x.seq <- seq(0,60,0.01)
y.LO.inva <- fun.all(x.seq,1)
plot(x.seq, y.LO.inva, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Invasive LO",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LO.xy.inva$x),c(0,LO.xy.inva$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of DCIS LO
```{r results = 'asis'}
y.LO.dcis <- fun.all(x.seq,2)
plot(x.seq, y.LO.dcis, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of DCIS LO",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LO.xy.dcis$x),c(0,LO.xy.dcis$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Contralateral LO
```{r results = 'asis'}
y.LO.con <- fun.all(x.seq,3)
plot(x.seq, y.LO.con, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Contralateral LO",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LO.xy.con$x),c(0,LO.xy.con$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Invasive LRT
```{r results = 'asis'}
x.seq <- seq(0,60,0.01)
y.LRT.inva <- fun.all(x.seq,4)
plot(x.seq, y.LRT.inva, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Invasive LRT",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LRT.xy.inva$x),c(0,LRT.xy.inva$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of DCIS LRT
```{r results = 'asis'}
y.LRT.dcis <- fun.all(x.seq,5)
plot(x.seq, y.LRT.dcis, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of DCIS LRT",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LRT.xy.dcis$x),c(0,LRT.xy.dcis$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Contralateral LRT
```{r results = 'asis'}
y.LRT.con <- fun.all(x.seq,6)
plot(x.seq, y.LRT.con, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Contralateral LRT",lty=1,type='l',pch=1,col="red")
par(new=TRUE)
plot(c(0,LRT.xy.con$x),c(0,LRT.xy.con$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```


**Then we use inverse transformation sampling to get the sampling result which have the above distribution.**
Here, type=1 means for cumulative incidence rate of Invasive LO

type=2 means for cumulative incidence rate of DCIS LO

type=3 means for cumulative incidence rate of Contralateral Invasive LO

type=4 means for cumulative incidence rate of Invasive LRT

type=5 means for cumulative incidence rate of DCIS LRT

type=6 means for cumulative incidence rate of Contralateral Invasive LRT


```{r results = 'asis'}
#get the inverse of these function
inver.LO.inva <- inverse(fun.LO.inva,lower=0,upper=60)
inver.LO.dcis <- inverse(fun.LO.dcis,lower=0,upper=60)
inver.LO.con <- inverse(fun.LO.con,lower=0,upper=60)

inver.LRT.inva <- inverse(fun.LRT.inva,lower=0,upper=60)
inver.LRT.dcis <- inverse(fun.LRT.dcis,lower=0,upper=60)
inver.LRT.con <- inverse(fun.LRT.con,lower=0,upper=60)

#check whether the inverse function is correct or not
#return a list of xvalue from the function
#1 for LO.inva
#2 for LO.dcis
#3 for LO.con
#4 for LRT.inva
#5 for LRT.dcis
#5 fot LRT.con
fun.inver <- function(u,type)
{
  if(type==1)
  {
    fun = inver.LO.inva
  }
  if(type==2)
  {
    fun = inver.LO.dcis
  }
  if(type==3)
  {
    fun = inver.LO.con
  }
  if(type==4)
  {
    fun = inver.LRT.inva
  }
  if(type==5)
  {
    fun = inver.LRT.dcis
  }
  if(type==6)
  {
    fun = inver.LRT.con
  }
  x.value <- rep(NA,length(u))
  for(j in 1:length(u))
  {
    x.value[j] <- fun(u[j])
  }
  return(x.value)
}
```


Then we compare empirical cdf from simulation to the true cdf and double check the inverse function is right or not

For Cumulative incidence rate of Invasive LO
```{r results = 'asis'}
y.seq <- runif(10000,0,1)
x.LO.inva <- fun.inver(y.seq,1)
plot(x.LO.inva, y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Invasive LO",lty=1,type='p',pch=1,col="red",
     ylim=c(0,1),xlim=c(0,60),cex=0.4)
par(new=TRUE)
plot(c(0,LO.xy.inva$x),c(0,LO.xy.inva$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of DCIS LO
```{r results = 'asis'}
x.LO.dcis <- fun.inver(y.seq,2)
plot(x.LO.dcis,y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of DCIS LO",lty=1,type='p',pch=1,col="red",
     ylim=c(0,1),xlim=c(0,60),cex=0.4)
par(new=TRUE)
plot(c(0,LO.xy.dcis$x),c(0,LO.xy.dcis$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Contralateral LO
```{r results = 'asis'}
x.LO.con <- fun.inver(y.seq,3)
plot(x.LO.con, y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Contralateral LO",lty=1,type='p',pch=1,col="red",
     ylim=c(0,1),xlim=c(0,60),cex=0.4)
par(new=TRUE)
plot(c(0,LO.xy.con$x),c(0,LO.xy.con$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Invasive LRT
```{r results = 'asis'}
x.LRT.inva <- fun.inver(y.seq,4)
plot(x.LRT.inva, y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Invasive LRT",lty=1,type='p',pch=0.6,col="red",
     ylim=c(0,1),xlim=c(0,60),cex=0.4)
par(new=TRUE)
plot(c(0,LRT.xy.inva$x),c(0,LRT.xy.inva$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of DCIS LRT
```{r results = 'asis'}
x.LRT.dcis <- fun.inver(y.seq,5)
plot(x.LRT.dcis, y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of DCIS LRT",lty=1,type='p',pch=0.6,col="red",
     ylim=c(0,1),xlim=c(0,60),cex=0.4)
par(new=TRUE)
plot(c(0,LRT.xy.dcis$x),c(0,LRT.xy.dcis$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

For Cumulative incidence rate of Contralateral LRT
```{r results = 'asis'}
x.LRT.con <- fun.inver(y.seq,6)
plot(x.LRT.con, y.seq, xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of Contralateral LRT",type='p',pch=0.6,
     ylim=c(0,1),xlim=c(0,60),col="red",cex=0.4)
par(new=TRUE)
plot(c(0,LRT.xy.con$x),c(0,LRT.xy.con$y/100),col="purple",pch=1,cex=0.6,xlab = "Years",
     ylab = "cumulative incidence",ylim=c(0,1),xlim=c(0,60))
legend("topleft",
       legend=c("Interpolation","Observed data"),
       col =c("red","purple"),inset=.02,cex=0.6,pch=1)
```

Simulate the trial arms: 
1.lumpectomy
2.lumpectomy + radiation
3.active surveillance. Rho=.19, psi=70%, beta=80%, lambda=.1/(5 years).


For LO
```{r results = 'asis'}
T <- seq(0,60,0.001)
plot(T, fun.all(T,3), xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of LO",lty=1,type='l',pch=1,col="red",ylim=c(0,1))
par(new=TRUE)
plot(T, fun.all(T,3)+fun.all(T,2), xlab = "Years",ylab = "cumulative incidence",
     lty=1,type='l',pch=1,col="purple",
     ylim=c(0,1))
par(new=TRUE)
plot(T, fun.all(T,1)+fun.all(T,2)+fun.all(T,3), xlab = "Years",ylab = "cumulative incidence"
     ,lty=1,type='l',pch=1,col="blue",
     ylim=c(0,1))

legend("topleft",
       legend=c("Contralateral Cancer","Contralateral Cancer+Ipsilateral DCIS",
                "Contralateral Cancer+Ipsilateral DCIS+Invasive"),
       col =c("red","purple","blue"),inset=.02,cex=0.3,pch=1)

#for any input T just use the cumulative probability of the three situation
T <- 1
fun.all(T,1)+fun.all(T,2)+fun.all(T,3)
```

For LRT
```{r results = 'asis'}
T <- seq(0,60,0.001)
plot(T, fun.all(T,6), xlab = "Years",ylab = "cumulative incidence",
     main = "Cumulative incidence rate of LRT",lty=1,type='l',pch=1,col="red",ylim=c(0,1))
par(new=TRUE)
plot(T, fun.all(T,5)+fun.all(T,6), xlab = "Years",ylab = "cumulative incidence",
     lty=1,type='l',pch=1,col="purple",
     ylim=c(0,1))
par(new=TRUE)
plot(T,fun.all(T,4)+fun.all(T,5)+fun.all(T,6), xlab = "Years",ylab = "cumulative incidence",
     lty=1,type='l',pch=1,col="blue",
     ylim=c(0,1))
legend("topleft",
       legend=c("Contralateral Cancer","Contralateral Cancer+Ipsilateral DCIS",
                "Contralateral Cancer+Ipsilateral DCIS+Invasive"),
       col =c("red","purple","blue"),inset=.02,cex=0.3,pch=1)
#for any input T just use the cumulative probability of the three situation
T <- 1
fun.all(T,4)+fun.all(T,5)+fun.all(T,6)
```

For AS
```{r results = 'asis'}
setwd("~/COMET_trial/COMET_trial_simulation/COMET_trial_6_12")
source("AS functions.R")
T <- 1
cum.cal(ti=T,deltat=3/12,N7=10000,n.sim = 50,beta=0.8,psi=0.7,rho=0.19,lambda=0.1)
```


Simulation of trials: for each woman, record time of first event, and type of first event. 
Then compare “ipsilateral invasive cancer-free survival”, starting with a Kaplan Meier analysis. start with simulate 10000 women
For LO
```{r results = 'asis'}
N <- 10000
y.seq <- runif(N,0,1)
#for ipsilateral invasive cancer recurrence
LO.inva <- fun.inver(y.seq,1)
#for ipsilateral dcis recurrence
LO.dcis <- fun.inver(y.seq,2)
#for Contralateral recurrence
LO.con <- fun.inver(y.seq,3)
LO.time_to_event <- rep(NA,N)
LO.type_event <- rep(NA,N)
for (i in 1:N)
{
  LO.time_to_event[i] <- min(LO.inva[i],LO.dcis[i],LO.con[i])
  if (LO.time_to_event[i]==LO.inva[i])
  {
    LO.type_event[i] <- "Ipsilateral Invasive"
  }
  if (LO.time_to_event[i]==LO.dcis[i])
  {
    LO.type_event[i] <- "Ipsilateral DCIS"
  }
  if (LO.time_to_event[i]==LO.con[i])
  {
    LO.type_event[i] <- "Contralateral Cancer"
  }
}
```


for LRT
```{r results = 'asis'}
#for ipsilateral invasive cancer recurrence
LRT.inva <- fun.inver(y.seq,4)
#for ipsilateral dcis recurrence
LRT.dcis <- fun.inver(y.seq,5)
#for Contralateral recurrence
LRT.con <- fun.inver(y.seq,6)
LRT.time_to_event <- rep(NA,N)
LRT.type_event <- rep(NA,N)

for (i in 1:N)
{
  LRT.time_to_event[i] <- min(LRT.inva[i],LRT.dcis[i],LRT.con[i])
  if (LRT.time_to_event[i]==LRT.inva[i])
  {
    LRT.type_event[i] <- "Ipsilateral Invasive"
  }
  if (LRT.time_to_event[i]==LRT.dcis[i])
  {
    LO.type_event[i] <- "Ipsilateral DCIS"
  }
  if (LRT.time_to_event[i]==LO.con[i])
  {
    LRT.type_event[i] <- "Contralateral Cancer"
  }
}
```

Ipsilateral invasive cancer-free survival

For LO
```{r results = 'asis'}
T <- seq(0,60,0.001)
set.seed(2)
ss.LO <- LO.time_to_event
gg.LO <- factor(LO.type_event,c("Ipsilateral Invasive","Ipsilateral DCIS","Contralateral Cancer"))
print(xx.LO <- cuminc(ss.LO,gg.LO))
plot(T, 1-fun.all(T,1),
     main = "Ipsilateral invasive cancer-free survival of LO",lty=1,type='l',xlab="Years",
     ylab="Probability",
     pch=1,col=1,ylim=c(0,1))
par(new=TRUE)
plot(xx.LO$`1 Ipsilateral Invasive`$time,1-xx.LO$`1 Ipsilateral Invasive`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Probability",main="Ipsilateral invasive cancer-free survival of LO",
     ylim=c(0,1))
legend("topright",
       legend=c("Considering Competing risk","Not considering competing risk"),
       col =c("red","black"),inset=.02,cex=0.5,pch=1)
```

For LRT
```{r results = 'asis'}
T <- seq(0,60,0.001)
set.seed(2)
ss.LRT <- LRT.time_to_event
gg.LRT <- factor(LRT.type_event,c("Ipsilateral Invasive","Ipsilateral DCIS","Contralateral Cancer"))
print(xx.LRT <- cuminc(ss.LRT,gg.LRT))
plot(T, 1-fun.all(T,4),
     main = "Ipsilateral invasive cancer-free survival of LRT",lty=1,type='l',xlab="Years",
     ylab="Probability",
     pch=1,col=1,ylim=c(0,1))
par(new=TRUE)
plot(xx.LRT$`1 Ipsilateral Invasive`$time,1-xx.LRT$`1 Ipsilateral Invasive`$est,lty=1,col="red",type="l",
     xlab="Years",ylab="Probability",main="Ipsilateral invasive cancer-free survival of LRT",
     ylim=c(0,1))
legend("topright",
       legend=c("Considering Competing risk","Not considering competing risk"),
       col =c("red","black"),inset=.02,cex=0.5,pch=1)

```


For AS
```{r results = 'asis'}
T <- seq(0.5,60,0.5)
fun.AS <- function(u)
{
  AS.value <- rep(NA,length(u))
  for(j in 1:length(u))
  {
    AS.value[j] <- cum.cal(ti=u[j],deltat=0.5,N7=10000,n.sim = 1,
                           beta=0.8,psi=0.7,rho=0.19,lambda=0.1)$mean.pro
  }
  return(AS.value)
}

plot(T, 1-fun.AS(c(T)),
     main = "Ipsilateral invasive cancer-free survival of AS",lty=1,type='l',xlab="Years",
     ylab="Probability",
     pch=1,col=1,ylim=c(0,1))
```





